A full approximation scheme multilevel method \\ for nonlinear variational inequalities

### 2024-01-10 paper/fascd.tex
table 4 preproduced
add zenodo to code availability; we should be set for reproducibility badge

% see git@bitbucket.org:pefarrell/fascd.git: examples/pollutant.py
% and reproduce/table4.py
\begin{table}[ht]
\centering
\begin{tabular}{lr@{\hskip 7mm}c@{\hskip 4mm}c}
\toprule
\emph{levels} & $m_J$ & $d=2$ & $d=3$ \\
\midrule
 2 &    $31^d$ & +1 & +1 \\
 3 &    $61^d$ & +1 & +1 \\
 4 &   $121^d$ & +1 & +1 \\
 5 &   $241^d$ & +1 & +2 \\
 6 &   $481^d$ & +1 \\
 7 &   $961^d$ & +2 \\
 8 &  $1921^d$ & +2 \\
 9 &  $3841^d$ & +2 \\
\bottomrule
\end{tabular}
\bigskip
\caption{FMG cycle results for 2D ($P_1$, serial) and 3D ($Q_1$, 16 processes) solutions of Example \ref{ex:results:advdiff}.}
\label{tab:results:advdiff}
\end{table}

@@

\subsection*{Code availability} \label{sec:code}  The software used to produce the results is archived at tag \texttt{v1.0} in the repository \texttt{\url{https://bitbucket.org/pefarrell/fascd/}}, using Firedrake version \texttt{3fb16ad47}.

>>>>

% see git@bitbucket.org:pefarrell/fascd.git: examples/pollutant.py
% and reproduce/table4.py
\begin{table}[ht]
\centering
\begin{tabular}{lr@{\hskip 7mm}c@{\hskip 4mm}c}
\toprule
\emph{levels} & $m_J$ & $d=2$ & $d=3$ \\
\midrule
 2 &    $31^d$ & +1 & +1 \\
 3 &    $61^d$ & +1 & +1 \\
 4 &   $121^d$ & +1 & +1 \\
 5 &   $241^d$ & +1 & +2 \\
 6 &   $481^d$ & +1 &  \\
 7 &   $961^d$ & +2 &  \\
 8 &  $1921^d$ & +2 &  \\
 9 &  $3841^d$ & +2 &  \\
\bottomrule
\end{tabular}
\bigskip
\caption{FMG cycle results for 2D ($P_1$, serial) and 3D ($Q_1$, 16 processes) solutions of Example \ref{ex:results:advdiff}.}
\label{tab:results:advdiff}
\end{table}

@@

\subsection*{Code availability} \label{sec:code}  The software used to produce the results in Section \ref{sec:results} is archived at tag \texttt{v1.0} in the repository \texttt{\url{https://bitbucket.org/pefarrell/fascd/}} and at \href{https://doi.org/10.5281/zenodo.10476845}{\texttt{doi:10.5281/zenodo.10476845}}.  We used Firedrake master revision \texttt{c5e939dde}.
